Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-07-31 manuscript/manuscript.tex
adds new results from upping the perturbation percentages for climate

Forecasting future states of populations has taken on new urgency as the
rate of climate change increases. Traditional plant population models
have limited utility in this regard because they are based on detailed
demographic data from small, localized plots. These models are difficult
to scale up to spatial scales relevant to land managers that require
such forecasts to make decisions. To overcome the data limitations of
traditional population models, some have proposed population models
based on population level, rather than individual level, data that is
much easier to collect over broad spatial scales. Using such models
violates a central assumption of ecology: individuals respond to
weather, not populations to climate. Here, we test whether this
assumption is important when forecasting climate change impacts on four
perennial grass species in a semi-arid Montana grassland. We
parameterized two population models, one based on inidividual-level data
with three vital rates and one on population-level data from the same
dataset (percent cover of quadrats), and compared their accuracy,
precision, and sensitivity to climate. The individual level model was
more accurate and precise than the aggregate level model when predicting
out-of-sample observations. When comparing climate effects from both
models, the population-level model tends to ``miss'' important climate
effects from at least one vital rate for each species. We also find that
increasing the sample size at the population-level would not necessarily
reduce forecast certainty; meaning the only way to reduce uncertainty is
to capture unique climate dependence on individual vital rates. It
appears there is no short cut to forecasting climate change impacts on
plant populations --- detailed demographic data is essential. However,
forecasts from our individual-level model were very uncertain, so we
advocate for a focus on new methods to collect demographic data more
efficiently across environmental gradients in space and time.

@@

Perhaps the greatest challenge for ecology in the 21st century is to
forecast the impacts of environmental change (Clark et al. 2001, Petchey
et al. 2015). To do so requires sophisticated modeling approaches that
fully account for uncertainty and variability in the ecological process
and associated parameters (Luo et al. 2011). This requires large amounts
of data collected over large spatio-temporal extents.
State-of-the-science modeling techniques cannot overcome data
limitations. Such is the case for many population models.

Population models are important tools for predicting the impacts of
environmental change on species persistence and abundance. But
reconciling the scales at which population models are parameterized and
the scales at which environmental changes play out remains a challenge
(Clark et al. 2010, 2012, Freckleton et al. 2011, Queenborough et al.
2011). The major hurdle is that most population models are built using
data from a single study site because collecting those data, which
involves tracking the fates of individuals plants, is so difficult. The
resulting models cannot be applied to the landscape and regional scales
relevant to decision-makers without information about how the fitted
parameters respond to spatial variation in biotic and abiotic drivers
(Sæther et al. 2007). The limited spatial extent of individual-level
demographic datasets constrains our ability to use population models to
address applied questions about the consequences of climate change.

The inability of many population models to address landscape-scale
problems may explain why land managers and conservation planners have
embraced species distribution models (SDMs) (see Guisan and Thuiller
2005 for a review). SDMs typically rely on easy-to-collect
presence/absence data (but see Clark et al. 2014 for new methods) and
remotely-sensed environmental covariates that allow researchers to model
large spatial extents (e.g., Maiorano et al. 2013). Thus, it is
relatively straightforward to parameterize and project SDMs over
landscapes and regions, the scales at which many land-use decisions are
made. However, the limitations of SDMs are well known (Pearson and
Dawson 2003, Elith and Leathwick 2009, Araújo and Peterson 2012).
Ideally, researchers would provide managers with landscape-scale
population models, combing the extent of SDMs with information about
dynamics and species abundances.

@@

Building on Taylor and Hastings (2004), Freckleton et al. (2011) showed
that density-structured models compare well to continuous models in
theory, and Queenborough et al. (2011) demonstrated the application of
such methods in a study on arable weeds. In particular, Queenborough et
al. (2011) provide empirical evidence that density-structured models are
capable of reproducing population dynamics, even if some precision is
lost when compared to fully continuous models. The study by Queenborough
et al. (2011) included data from 500 fields (4 hectares each) in 49
farms, all collected by two people in 6 weeks. This is far more data
from a far greater spatial extent than possible if measuring individual
plant demography (in a world of limited time and money, at least). The
appeal of density-structured approaches is clear. However, none of these
models included environmental covariates.

Addressing climate change questions with models fit to population-level
data is potentially problematic. It is individuals, not populations,
that respond to climate variables (Clark et al. 2012). Ignoring this
fact puts us in uneasy proximity to an ``ecological fallacy'', where
inference about the individual relies on statistical inference on the
group (Piantadosi et al. 1988). Population growth (or decline) is an
epiphenomenon of demographic processes like survival, growth, and
recruitment that occur at the level of individual plants. Climate can
affect each demographic process in unique, potentially opossing, ways
(Dalgleish et al. 2011). These unique climate responses may difficult
resolve in statistical models based on population-level data where
demographic processes are not identifiable. If population-level data
cannot detect important impacts of climate drivers on populations, then
population models built with such data will make poor forecasts.

Here, we ask whether statistical and population models based on
aggregated, population-level data can detect climate signals as wells as
models based on individual-level data. We used a unique demographic
dataset that tracks the fates of individual plants from four species
over 14 years to build two kinds of single-species population models,
traditional models using individual growth, survival, and recruitment
data and alternative models based on basal cover. In both models,
interannual variation is explained, in part, by climate covariates. We
then performed simulations to quantify the sensitivities of species'
cover to small perturbations in average precipitation and temperature.
We found that population models based on detailed demographic data are
more accurate and precise than models based on aggregated data. Our
results suggest the popuation-level model is less accurate and precise
because important demographic climate signals go undetected. For these
species at this location, detailed demographic data appears necessary to
make accurate forecasts. A worrying caveat to our work is that forecasts
from both models were very uncertain when we considered full process and
parameter uncertainty. Even 14 years worth of demographic data may not
be sufficient to make useful forecasts.

@@

From 1932 to 1945 individual plants were identified and mapped annually
in 44 1-$\text{m}^2$ quadrats using a pantograph. The quadrats were
distributed in six pastures, each assigned a grazing treatment of light
(1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy (0.76
ha/aum) stocking rates (two pastures per treatment). In this analysis we
account for potential differences among the grazing treatments, but do
not focus on grazing$\times$climate interactions. The annual maps of the
quadrats were digitized and the fates of individual plants tracked and
extracted using a computer program (Lauenroth and Adler 2008, Chu et al.
2014). Daily climate data, which we aggregated into climate variables of
interest, are available for the duration of the data collection period
(1932 - 1945) from the Miles City airport, Wiley Field, 9 km from the
study site.

@@

At both levels of inference (individual and quadrat), the building
blocks of our population models are vital rate regressions. For
individual-level data we fit models for survival, growth, and
recruitment for each species. At the quadrat-level we fit a single
regression model for population growth. We describe the statistical
models separately since fitting the models required different
approaches. All models contain five climate covariates that we chose
\emph{a priori}: ``water year'' precipitation at \emph{t}-1 (lagppt);
April through June precipitation at \emph{t}-1 and \emph{t}-2 (ppt1 and
ppt2, respectively) and April through June temperature at \emph{t}-1 and
\emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t} is
the observation year. We also include interactions among same-year
climate covariates (e.g., ppt1 $\times$ TmeansSpr1) and climate $\times$
size interactions. Climate $\times$ size interactions are for climate
main effects only, that is we do not include interactions among size and
interacting climate effects.

@@

We modeled growth as Gaussian process describing genet size at time
$t+1$ as a function of size at $t$ and climate covariates:

\begin{align}
x_{ijQ,t+1} &= \gamma^{G}_{j,t} + \phi^{G}_{jQ} + \beta^{G}_{j,t}x_{ij,t} + \omega^{G}_{j}w_{ij,t} + \nu^{S}_{j}w_{ij,t}x_{ij,t} + \theta^{G}_{jk}C_{k,t} \\
y^{G}_{ijQ,t} &\sim \text{Normal}(x_{ijQ,t+1}, \sigma_{j})
\end{align}

where $x$ is log genet size and all other parameters are as described
for the survival regression.

@@

All of our analyses (model fitting and simulating) were conducted in R
(R Core Development Team 2013). We used the `No-U-Turn' MCMC sampler in
Stan (Stan Development Team 2014a) to estimate the posterior
distributions of model parameters using the package `rstan' (Stan
Development Team 2014b). We obtained posterior distributions for all
model parameters from three parallel MCMC chains run for 1,000
iterations after discarding an initial 1,000 iterations. We recignize
such short MCMC chains may surprise those more familiar with other MCMC
samplers (i.e.~JAGS or WinBUGS), but the Stan sampler is exceptionally
efficient, which reduces the number of iterations needed to achieve
convergence. We assessed convergence visually and made sure scale
reduction factors for all parameters were less than 1.01. For the
purposes of including parameter uncertainty in our population models, we
saved the final 1,000 iterations from each of the three MCMC chains to
be used as randomly drawn values during population simulation. This step
alleviates the need to reduce model parameters by model selection since
sampling from the full parameter space in the MCMC ensures that if a
parameter broadly overlaps zero, on average the effect in the population
models will also be near zero. We report the posterior mean, standard
deviation, and 95\% Bayesian Credible Intervals for every parameter of
each model for each species in Appendix B.

@@

With the posterior distribution of the vital rate statistical models in
hand, it is straightforward to simulate the population models. We used
an Integral Projection Model (IPM) to model populations based on
individual level data {[}cite Ellner and Rees 2006{]} and an quadrat
based version of an individually-based model (Quadrat-Based Model, QBM)
to model populations based on quadrat level data. We describe each in
turn.

@@

We use an environmentally stochastic IPM (Rees and Ellner 2009) that
includes the random year effects and the climate covariates from the
vital rate statistical models. However, for some simulations, we ignore
the random year effects so that only the climate effects drive
interannual variation. Our IPM follows the specification of Chu and
Adler (2015) where the population of species \emph{j} is a density
function $n(u_{j},t)$ giving the density of sized-\emph{u} genets at
time \emph{t}. Genet size is on the natural log scale, so that
$n(u_{j},t)du$ is the number of genets whose area (on the arithmetic
scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. So, the density
function for any size \emph{v} at time $t+1$ is

@@

@@

which means we are calculating growth (\emph{G}) for individuals that
survive (\emph{S}) from time \emph{t} to \emph{t+1} and adding in newly
recruited (\emph{R}) individuals of an average sized one-year-old genet
for the focal species. Our stastical model for recruitment (\emph{R},
described above) returns the number of new recruit produced per quadrat.
Following previous work (Adler et al. 2012, Chu and Adler 2015), we
assume that fecundity increases linearly with size
($R_j(v_{j},u_{j},\bar{\bold{w_{j}}}) = e^{u_j}R_j(v_{j},\bar{\bold{w_{j}}})$)
to incorporate the recruitment function in the spatially-implicit IPM.
\todo{Add spatial structure mention.}

@@

Our quad-based model (QBM) perfectly mirrors its statistical description
(Eqs. 8-9). We use the same approach for drawing parameter values as
described for the IPM. After drawing the appropriate parameter set, we
calculate the mean response (population cover at \emph{t+1} = $x_{t+1}$)
according to Eq. 8. We then make a random draw from a {[}0,1{]}
truncated lognormal distribution with mean equal to $x_{t+1}$ from Eq. 8
and the variance estimate from the fitted model. We can then iterate the
model forward by drawing a new parameter set (unique to climate year and
MCMC iteration) at each timestep.

@@

Our main goal in this paper is to see if models based on aggregated data
are as sensitive to climate covariates as models based on individual
level data. So, with our fitted and validated models in hand, we ran
simulations for each model type (IPM and QBM) under four climate
perturbation scenarios: (1) observed climate, (2) precipitation
increased by 1\%, (3) temperature increased by 1\%, and (4)
precipitation and temperature increased by 1\%. We ran the simulations
for 2,500 time steps, enough to estimate equilibrium cover after
discarding an initial 500 time steps as burn-in. Each simulation was run
under two parameter scenarios: (1) using mean parameter estimates and
(2) using randomly drawn parameters from the MCMC chain. We use (1) to
detect the overall sensitivity of equilibrium cover to climate, and we
use (2) to show the impact of model and parameter uncertainty on
forecast precision.

@@

Our expectation is that the IPM will produce more accurate and precise
forecasts. This could be due to differences in sample sizes leading to
larger parameter uncertainty for the QBM, or due to the QBM climate
effects being weakly associated with one or more vital rate climate
effects at the individual level. To assess the impact of sample size on
QBM parameter uncertainty we refit the QBM statistical model (Eqs. 8-9)
after removing sets of 2, 5, 10, and 15 quadrats. We fit 10 models at
each level of quadrat removal (2, 5, 10, 15 quadrats), removing a
different randomly selected set of quadrats for each fit. We calculated
the standard deviation of climate main effects (pptlag, ppt1, ppt2,
TmeanSpr1, and TmeanSpr2) for each model and averaged those over
replicates within each set of quadrat removals. This allowed us to
regress sample size against parameter uncertainty.

To see if the QBM climate effects are correlated, or not, with climate
effects for each vital rate model for the IPM, we simply regressed the
QBM climate coefficients against each vital rate model's climate
coefficients and calculate Pearson's $\rho$. Strong correlations
indicate the QBM is capable of detecting climate effects associated with
individual vital rates. A weak correlation indicates the QBM ``misses''
the climate effect on a particular vital rate.

@@

The response of a population to climate change is a result of the
aggregate effects of climate on individual vital rates. Since the IPM
approach relies on vital rate regressions, we were able to quantify the
sensitivity of each vital rate in isolation and in pairwise
combinations. Across all species, climate covariates can have opposing
effects on different vital rates (Fig. 3). Growth was the most sensitive
vital rate for all species, showing a negative response to increased
precipitation, and stronger positive response to increased temperature,
and a mostly positive response when both climate factors are increased
(Fig. 3). \emph{B. gracilis} survival rates were sensitive to
temperature, resulting in an increase in plant cover under increased
temperature (Fig. 3a). In isolation, recruitment and survival were
insensitive to climate factors for \emph{H. comata} (Fig. 3b). Survival
and recruitment of \emph{P. smithii} were both sensitive, negatively, to
temperature and precipitation (Fig. 3c). \emph{P. secunda} equilibrium
cover was sensitive to the climate effects on survival and recruitment,
showing a negative effect on both vital rates for increased precipition,
but a strong positive effect on survival with increased temperature
(Fig. 3d). The climate impact of recruitment on equilibrium cover was
negative for precipitation and temperature increases (Fig. 3d). At least
two of three vital rates were sensitive to climate for each species
(Fig. 3).

@@

Sample size had a relatively weak effect on QBM climate parameter
uncertainty after the number of quadrats exceeded about 10 (Fig. 5).
Inverse-gaussian fits show that increasing sample size beyond the number
of quadrats we used will results in deminishing returns in terms of
parameter certainty (Fig. 5).

@@

Forecasts based on 1\% climate changes were extremely uncertain when we
considered model error and parameter uncertainty (Fig. 6). As expected
based on model validation (Table 1), QBM projections were more uncertain
than IPM projections for all species except \emph{P. smithiii} (Fig. 6).
IPM forecasts for \emph{P. smithiii} were very uncertain due to
overcompensating density dependence and nonlinearities recruitment that
get amplified by parameter uncertainty (Appendx C). Neither model was
capable of making forecasts of proportional cover change distinguishable
from 0 (i.e., no change in population state) when we included model
error and parameter uncertainty.

@@

Population models built using individual-level data allow inference on
demographic processes, but their ability to forecast future population
states is limited by the spatial extent of the data. Population-level
data, like percent cover or discrete density states, are much easier to
collect of broad spatial extents, so populations built using such data
offer an appealing alternative to traditional population models
(Queenborough et al. 2011). However, at their core, density-structured
models rely on individual level data aggregated to a population level
metric. This creates a potential problem if such models are to be used
in a climate change context because inidividuals respond to climate, not
populations (Clark et al. 2012). Are models based on population level
metrics as sensitive to climate as models based on individual level
metrics? Do these two types of models produce consistent forecasts? Do
we need detailed demographic data to forecast the impacts of climate
change? These are the questions we sought to answer here.

Using individual-level and population-level forms of the same dataset,
we were able to directly compare a traditional demographic modeling
approach to a population model based on percent cover data. Our
quad-based model (QBM) is based on percent cover data and so is in the
spirit of density-structured models. In terms of each model's
forecasting ability, the IPM outperformed the QBM: the IPM was more
accurate and precise than the QBM (Table 1). As we suggest in the
introduction, this could be due to differences in sample size or the
effect of averaging over climate responses unique to individual-level
vital rates.

We found no evidence that increasing sample size at the quadrat level
would lead to higher precision of climate coefficient estimates (Fig.
4). We did, however, find evidence that the QBM statistical model failed
to identify climate dependence for some vital rates (Fig. 5). For no
species were climate effects from the QBM strongly correlated with all
three vital rates (Fig. 5). Freckleton et al. (2011) acknowledge that
averaging over complex stage dependence will lead to poorly specified
models. This is analagous to our situation, but instead of averaging
over complex life histories, we are averaging over complex climate
dependence.

Thus, for each species the QBM is ``missing'' climate signals associated
with at least one vital rate. This leads to inaccurate and imprecise
forecasts because the QBM statistical model struggles to explain
variation due to climate variables that have positive and negative
impacts on different vital rates. When this is the case, as it is for
all our species to varying degrees (Fig. 3), statistical models of
population-level data will fail. This result further confirms related
work on the importance of individual-level data to forecast population
responses to exogenous drivers (Clark et al. 2011a, 2011b, 2012, Galván
et al. 2014).

>>>>

Forecasting future states of populations has taken on new urgency as the
rate of climate change increases. Traditional plant population models,
typically built using detailed demographic observations from one study
site, can address climate change impacts at one location, but are
difficult to scale up to the landscape and regional scales relevant to
management decisions. One proposal to overcome the limitations of
traditional population models is to build models using population-level
data that is much easier to collect over broad spatial scales than
individual-level data. However, such models ignore the fact that climate
drives population growth through its influence on individual
performance. Here, we test the consequences of aggregating individual
responses when forecasting climate change impacts on four perennial
grass species in a semi-arid Montana grassland. We parameterized two
population models, one based on individual-level data (survival, growth
and recruitment) and one on population-level data from the same dataset
(percent cover of quadrats), and compared their accuracy, precision, and
sensitivity to climate. The individual level model was more accurate and
precise than the aggregate level model when predicting out-of-sample
observations. When comparing climate effects from both models, the
population-level model tends to ``miss'' important climate effects from
at least one vital rate for each species. Increasing the sample size at
the population-level would not necessarily reduce forecast uncertainty;
the way to reduce uncertainty is to capture unique climate dependence of
individual vital rates. Our analysis indicates that there is no short
cut to forecasting climate change impacts on plant populations ---
detailed demographic data is essential. Despite the superiority of the
individual-level model, the forecasts it generated still were too
uncertain to be useful for decision-makers. We need new methods to
collect demographic data more efficiently across environmental gradients
in space and time.

@@

Perhaps the greatest challenge for ecology in the 21st century is to
forecast the impacts of environmental change (Clark et al. 2001, Petchey
et al. 2015). Forecasts require sophisticated modeling approaches that
fully account for uncertainty and variability in both ecological process
and model parameters (Luo et al. 2011). This requires large amounts of
data collected over broad spatio-temporal extents, and
state-of-the-science modeling techniques cannot overcome data
limitations. Population models are a case in point.

Population models are important tools for predicting the impacts of
environmental change on species persistence and abundance. But
reconciling the scales at which population models are parameterized and
the scales at which environmental changes play out remains a challenge
(Clark et al. 2010, 2012, Freckleton et al. 2011, Queenborough et al.
2011). The problem is that most population models are built using data
from a single study site because collecting those data, which involves
tracking the fates of individuals plants, is so difficult. The resulting
models cannot be applied to the landscape and regional scales relevant
to decision-makers without information about how the fitted parameters
respond to spatial variation in biotic and abiotic drivers (Sæther et
al. 2007). The limited spatial extent of individual-level demographic
datasets constrains our ability to use population models to address
applied questions about the consequences of climate change.

The inability of most population models to address landscape-scale
problems may explain why land managers and conservation planners have
embraced species distribution models (SDMs) (see Guisan and Thuiller
2005 for a review). SDMs typically rely on easy-to-collect
presence/absence data (but see Clark et al. 2014 for new methods) and
remotely-sensed environmental covariates that allow researchers to model
large spatial extents (e.g., Maiorano et al. 2013). Thus, it is
relatively straightforward to parameterize and project SDMs over
landscapes and regions, the scales at which many land-use decisions are
made. However, the limitations of SDMs are well known (Pearson and
Dawson 2003, Elith and Leathwick 2009, Araújo and Peterson 2012).
Ideally, researchers would provide managers with landscape-scale
population models, combining the extent of SDMs with information about
dynamics and species abundances.

@@

Building on Taylor and Hastings (2004), Freckleton et al. (2011) showed
that density-structured models compare well to continuous models in
theory, and Queenborough et al. (2011) demonstrated the application of
such methods in a study on arable weeds. In particular, Queenborough et
al. (2011) provide empirical evidence that density-structured models are
capable of reproducing population dynamics, even if some precision is
lost when compared to fully continuous models. The study by Queenborough
et al. (2011) included data from 500 fields (4 hectares each) in 49
farms, all collected by two people in 6 weeks. This is far more data
from a far greater spatial extent than would be possible if measuring
individual plant demography (in a world of limited time and money). The
appeal of density-structured approaches is clear. However, none of these
models included environmental covariates.

Addressing climate change questions with models fit to population-level
data is potentially problematic. It is individuals, not populations,
that respond to climate variables (Clark et al. 2012). Ignoring this
fact amounts to an ``ecological fallacy'', where inference about the
individual relies on statistical inference on the group (Piantadosi et
al. 1988). Population growth (or decline) is the outcome of demographic
processes like survival, growth, and recruitment that occur at the level
of individual plants. Climate can affect each demographic process in
unique, potentially opossing, ways (Dalgleish et al. 2011). These unique
climate responses may be difficult to resolve in statistical models
based on population-level data where demographic processes are not
identifiable. If population-level data cannot detect important impacts
of climate drivers on populations, then population models built with
such data will make poor forecasts.

Here, we ask whether statistical and population models based on
aggregated, population-level data can predict climate change impacts as
wells as models based on individual-level data. We used a unique
demographic dataset that tracks the fates of individual plants from four
species over 14 years to build two kinds of single-species population
models, traditional models using individual growth, survival, and
recruitment data and alternative models based on basal cover. In both
models, interannual variation is explained, in part, by climate
covariates. We then performed simulations to quantify the sensitivities
of species' cover to small perturbations in average precipitation and
temperature. Individual level models were clearly better, but,
unfortunately, still too uncertain to inform management decisions.

@@

From 1932 to 1945 individual plants were identified and mapped annually
in 44 1-$\text{m}^2$ quadrats using a pantograph. The quadrats were
distributed in six pastures, each assigned a grazing treatment of light
(1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy (0.76
ha/aum) stocking rates (two pastures per treatment). In this analysis we
account for potential differences among the grazing treatments, but do
not focus on grazing$\times$climate interactions. The annual maps of the
quadrats were digitized and the fates of individual plants tracked and
extracted using a computer program (Lauenroth and Adler 2008, Chu et al.
2014). Daily climate data are available for the duration of the data
collection period (1932 - 1945) from the Miles City airport, Wiley
Field, 9 km from the study site.

@@

At both levels of inference (individual and quadrat), the building
blocks of our population models are vital rate regressions. For
individual-level data, we fit models for survival, growth, and
recruitment for each species. At the quadrat-level, we fit a single
regression model for population growth. We describe the statistical
models separately since fitting the models required different
approaches. All models contain five climate covariates that we chose
\emph{a priori}: ``water year'' precipitation at \emph{t}-1 (lagppt);
April through June precipitation at \emph{t}-1 and \emph{t}-2 (ppt1 and
ppt2, respectively) and April through June temperature at \emph{t}-1 and
\emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t} is
the observation year. We also include interactions among same-year
climate covariates (e.g., ppt1 $\times$ TmeansSpr1) and climate $\times$
size interactions. Climate $\times$ size interactions are for climate
main effects only; we do not include interactions between size and pairs
of interacting climate effects.

@@

We modeled growth as a Gaussian process describing genet size at time
$t+1$ as a function of size at $t$ and climate covariates:

\begin{align}
x_{ijQ,t+1} &= \gamma^{G}_{j,t} + \phi^{G}_{jQ} + \beta^{G}_{j,t}x_{ij,t} + \omega^{G}_{j}w_{ij,t} + \nu^{S}_{j}w_{ij,t}x_{ij,t} + \theta^{G}_{jk}C_{k,t} \\
y^{G}_{ijQ,t} &\sim \text{Normal}(x_{ijQ,t+1}, \varepsilon_{ij,t})
\end{align}

where $x$ is log genet size and all other parameters are as described
for the survival regression. We capture non-constant error variance in
growth by modeling the variance around the growth regression
($\varepsilon$) as a nonlinear function of predicted genet size:

\begin{align}
\varepsilon_{ij,t} = a e^{b x_{ijQ,t+1}}
\end{align}

@@

All of our analyses (model fitting and simulating) were conducted in R
(R Core Development Team 2013). We used the `No-U-Turn' MCMC sampler in
Stan (Stan Development Team 2014a) to estimate the posterior
distributions of model parameters using the package `rstan' (Stan
Development Team 2014b). We obtained posterior distributions for all
model parameters from three parallel MCMC chains run for 1,000
iterations after discarding an initial 1,000 iterations. We recognize
such short MCMC chains may surprise those more familiar with other MCMC
samplers (i.e.~JAGS or WinBUGS), but the Stan sampler is exceptionally
efficient, which reduces the number of iterations needed to achieve
convergence. We assessed convergence visually and made sure scale
reduction factors for all parameters were less than 1.01. For the
purposes of including parameter uncertainty in our population models, we
saved the final 1,000 iterations from each of the three MCMC chains to
be used as randomly drawn values during population simulation. This step
alleviates the need to reduce model parameters by model selection since
sampling from the full parameter space in the MCMC ensures that if a
parameter broadly overlaps zero, on average the effect in the population
models will also be near zero. We report the posterior mean, standard
deviation, and 95\% Bayesian Credible Intervals for every parameter of
each model for each species in Appendix B.

@@

With the posterior distribution of the vital rate statistical models in
hand, it is straightforward to simulate the population models. We used
an Integral Projection Model (IPM) to model populations based on
individual level data (Ellner and Rees 2006) and a quadrat-based version
of an individually-based model (Quadrat-Based Model, QBM) to model
populations based on quadrat level data. We describe each in turn.

@@

We use an environmentally stochastic IPM (Rees and Ellner 2009) that
includes the climate covariates from the vital rate statistical models.
In all simulations we ignore the random year effects so that interannual
variation is driven solely by climate. We fit the random year effects in
the vital rate regressions to avoid over-attributing variation to
climate covariates. Our IPM follows the specification of Chu and Adler
(2015) where the population of species \emph{j} is a density function
$n(u_{j},t)$ giving the density of sized-\emph{u} genets at time
\emph{t}. Genet size is on the natural log scale, so that $n(u_{j},t)du$
is the number of genets whose area (on the arithmetic scale) is between
$e^{u_{j}}$ and $e^{u_{j}+du}$. The density function for any size
\emph{v} at time $t+1$ is

@@

Since the IPM is spatially-implicit, we cannot calculate neighborhood
crowding for specific genets ($w_{ij}$). Instead, we use an
approximation ($\bar{\bold{w_{j}}}$) that captures the essential
features of neighborhood interactions (Adler et al. 2010). We also use a
`no-overlap' rule for conspecific genets to approximate the
overdispersion of large genets in space (Adler et al. 2010, 2012, Chu
and Adler 2015).

@@

which means we are calculating growth (\emph{G}) for individuals that
survive (\emph{S}) from time \emph{t} to \emph{t+1} and adding in newly
recruited (\emph{R}) individuals of an average sized one-year-old genet
for the focal species. Our stastical model for recruitment (\emph{R},
described above) returns the number of new recruit produced per quadrat.
Following previous work (Adler et al. 2012, Chu and Adler 2015), we
assume that fecundity increases linearly with size
($R_j(v_{j},u_{j},\bar{\bold{w_{j}}}) = e^{u_j}R_j(v_{j},\bar{\bold{w_{j}}})$)
to incorporate the recruitment function in the spatially-implicit IPM.

@@

Our quad-based model (QBM) perfectly mirrors its statistical description
(Eqs. 9-10). We use the same approach for drawing parameter values as
described for the IPM. After drawing the appropriate parameter set, we
calculate the mean response (population cover at \emph{t+1} = $x_{t+1}$)
according to Eq. 9. We then make a random draw from a {[}0,1{]}
truncated lognormal distribution with mean equal to $x_{t+1}$ from Eq. 9
and the variance estimate from the fitted model. We can then project the
model forward by drawing a new parameter set (unique to climate year and
MCMC iteration) at each timestep. As with the IPM, random year effects
are ignored for all simulations.

@@

To see if models based on aggregated data are as sensitive to climate
covariates as models based on individual level data. So, with our fitted
and validated models in hand, we ran simulations for each model type
(IPM and QBM) under four climate perturbation scenarios: (1) observed
climate, (2) precipitation increased by 1\%, (3) temperature increased
by 1\%, and (4) precipitation and temperature increased by 1\%. We ran
the simulations for 2,500 time steps, enough to estimate equilibrium
cover after discarding an initial 500 time steps as burn-in. Each
simulation was run under two parameter scenarios: (1) using mean
parameter estimates and (2) using randomly drawn parameters from the
MCMC chain. We use (1) to detect the overall sensitivity of equilibrium
cover to climate, and we use (2) to show the impact of model and
parameter uncertainty on forecast precision.

@@

Our expectation is that the IPM will produce more accurate and precise
forecasts. This could be due to (1) the smaller sample size of the
quadrat level data sets compared to the individual level data sets,
leading to larger parameter uncertainty for the QBM, or (2) the QBM
climate effects being weakly associated with one or more vital rate
climate effects at the individual level. To assess the impact of sample
size on QBM parameter uncertainty we refit the QBM statistical model
(Eqs. 9-10) after removing sets of 2, 5, 10, and 15 quadrats. We fit 10
models at each level of quadrat removal (2, 5, 10, 15 quadrats),
removing a different randomly selected set of quadrats for each fit. We
calculated the standard deviation of climate main effects (pptLag, ppt1,
ppt2, TmeanSpr1, and TmeanSpr2) for each model and averaged those over
replicates within each set of quadrat removals. This allowed us to
regress sample size against parameter uncertainty.

To see if the QBM climate effects are correlated, or not, with climate
effects for each vital rate model for the IPM, we simply regressed the
QBM climate coefficients against each vital rate model's climate
coefficients and calculated Pearson's $\rho$. Strong correlations
indicate the QBM is capable of detecting climate effects associated with
individual vital rates. A weak correlation indicates the QBM ``misses''
the climate effect on a particular vital rate.

@@

The response of a population to climate change is a result of the
aggregate effects of climate on individual vital rates. Since the IPM
approach relies on vital rate regressions, we were able to quantify the
sensitivity of each vital rate in isolation and in pairwise
combinations. Across all species, climate covariates can have opposing
effects on different vital rates (Fig. 3). Growth was the most sensitive
vital rate for all species, showing a negative response to increased
precipitation, and stronger positive response to increased temperature,
and a mostly positive response when both climate factors are increased
(Fig. 3). \emph{B. gracilis} survival rates were sensitive to
temperature, resulting in an increase in plant cover under increased
temperature (Fig. 3a). In isolation, recruitment and survival were
insensitive to climate factors for \emph{H. comata} (Fig. 3b). Survival
and recruitment of \emph{P. smithii} were both sensitive, negatively, to
temperature and precipitation (Fig. 3c). \emph{P. secunda} equilibrium
cover was sensitive to the climate effects on survival and recruitment,
showing a negative effect on both vital rates for increased precipition,
but a strong positive effect on survival with increased temperature
(Fig. 3d). Equilibrium cover responded negatively when increased
precipitation and temperature affect recruitment (Fig. 3d). At least two
of three vital rates were sensitive to climate for each species (Fig.
3).

@@

Sample size had a relatively weak effect on QBM climate parameter
uncertainty after the number of quadrats used in fitting exceeded about
10 (Fig. 5). Inverse-gaussian fits show that increasing sample size
beyond the number of quadrats we used would result in diminishing
returns in terms of parameter certainty (Fig. 5).

@@

Forecasts based on 1\% climate changes were extremely uncertain when we
considered model error and parameter uncertainty (Fig. 6; simulations
with mean parameters are in Appendix D for comparison). As expected
based on model validation (Table 1), QBM projections were more uncertain
than IPM projections for all species except \emph{P. smithiii} (Fig. 6).
IPM forecasts for \emph{P. smithiii} were very uncertain due to a very
high instrinsic rate of recruitment combined with uncertainty in climate
coefficients which lead to high recruitment boom years and subsequent
busts when young plants suffer high mortality (Appendx C). When we
included model error and parameter uncertainty, forecast changes in
proportional cover always spanned a wide range of negative to positive
values. In other words, neither model could predict whether a climate
perturbation would increase or decrease equilibrium population size.

@@

Population models built using individual-level data allow inference on
demographic processes, but they can only forecast future population
states across the (typically limited) spatial extent of the
observations. Population-level data are much easier to collect across
broad spatial extents, so models built using such data offer an
appealing alternative to traditional population models (Queenborough et
al. 2011). However, density-structured models rely on the aggregation of
individual level data. This creates a potential problem if such models
are to be used in a climate change context because it is individuals,
not populations, which respond to climate (Clark et al. 2012). Are
models based on population level metrics as sensitive to climate as
models based on individual level metrics? Do these two types of models
produce consistent forecasts? Do we need detailed demographic data to
forecast the impacts of climate change?

\subsubsection{The importance of demographic
data}\label{the-importance-of-demographic-data}

Our comparison of a traditional, demographic population model (the IPM)
with a model inspired by density-structured models (the QBM) showed that
the IPM outperformed the QBM: the IPM was more accurate and precise than
the QBM in out-of-sample cross validation (Table 1). The superiority of
the IPM could reflect either differences in sample size or the effect of
averaging over unique effects of climate on each individual-level vital
rate. Although increasing sample size of quadrat percent-cover
observations would be easy to do in the field, we found little evidence
that it would lead to higher precision of climate coefficient estimates
(Fig. 4). We did, however, find evidence that the QBM statistical model
failed to identify climate dependence for some vital rates (Fig. 5). For
no species were climate effects from the QBM strongly correlated with
all three vital rates (Fig. 5). Freckleton et al. (2011) acknowledge
that averaging over complex stage dependence will lead to poorly
specified models. This is analagous to our situation, but instead of
averaging over complex life histories, we are averaging over complex
climate dependence.

Our interpretation is that the QBM is ``missing'' climate signals
associated with at least one vital rate for each species. This leads to
inaccurate and imprecise forecasts because the QBM statistical model
struggles to explain variation due to climate variables that have
positive and negative impacts on different vital rates. When this is the
case, as it is for all our species to varying degrees (Fig. 3),
statistical models of population-level data will fail. Our result is
consistent with related work on the importance of individual-level data
to forecast population responses to exogenous drivers (Clark et al.
2011a, 2011b, 2012, Galván et al. 2014).

Detailed demographic data appears to be necessary to forecast climate
change impacts on plant populations when vital rates have unique climate
responses. How then can we build models to make forecasts for the
landscape and regional scales beyond the scope of traditional population
models (Queenborough et al. 2011)? There are alternatives to
density-structured models. For example, Clark et al. (2011a) use Forest
Inventory and Analysis (FIA) data to parameterize a population model
with multiple vital rates and climate dependence. Distributed efforts
such as PlantPopNet (\url{http://plantago.plantpopnet.com}) will allow
researchers to estimate variation around climate responses for
widespread species by taking advantage of spatial variation in climate
(e.g. Doak and Morris 2010). Finally, new approaches on the horizon that
leverage photo/video of plots and advanced object recognition algorithms
(e.g. Liu et al. 2014) will increase the efficiency of plant mapping and
digitizing efforts.

\subsubsection{The challenge of
uncertainty}\label{the-challenge-of-uncertainty}
